Title

### 2013-04-02 inc/design_considerations/considerations.tex
begin merging Andreas' comments on considerations section

In Chapters \ref{chap:previous_models} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effects that column elements have upon it.
However, microscopy is an experimental science, and designing a UEM is no less hands-on.

When designing a UEM system, special care must be given to the creation and propagation of the electron beam.
In the case of single-shot UEM, several factors lead to two major considerations: first, that a large area photoemission source is preferred to smaller area or even single point emitters, and second, the transverse emittance of the beam must be minimized.

These considerations drive the remainder of this thesis.
In this chapter, I will first convince the reader of these considerations.
As a direct consequence of these considerations, it is our belief that a successful UEM project cannot simply stem from small modifications to the platform of a conventional electron microscope.
In the following chapters I will show how we are addressing these considerations for the prototype system at UIC, both in column design (Chapter \ref{chap:prototype}) and photocathode engineering (Chapter \ref{chap:photocathode}).

@@

In a conventional electron microscope the electrons are generated by one of several processes, often by heating the cathode or applying a large field to the cathode, or combinations thereof.
Although these processes produce a very large number of electrons, far more than required by the Rose criterion, they are essentially non-directional.
A pinhole is used to eliminate most of the electrons with the exception of those which will travel down the column, reducing the beam current but producing a high-quality beam. %TODO ref(s)

In fact, for conventional electron microscopes without time resolution, the Rose criterion may be met for even very low beam current by simply allowing the image to acquire for a long enough time to collect sufficent electrons.
Further, high beam current may be damaging to the sample over time, so a lower beam current is often preferred.

By definition, for single-shot imaging with a DTEM, all of these electrons must be contained in a single pulse.
Although sample damage concerns may be neglected, destructive measurements will result in useful images, the use of a pinhole is likely to reduce the pulse charge below the useful level.
This means that the designer of a DTEM must endeavor to retain and utilize all of the generated electrons.

>>>>

In Chapters \ref{chap:previous_models} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effects that column elements have upon it.
However, microscopy is an experimental science, and designing a UEM is no less hands-on.
%TODO avoid repitition? "When doing so, special ..."?
When designing a UEM system, special care must be given to the creation and propagation of the electron beam.
%TODO define single-shot and transverse emittance here or rephrase?
In the case of single-shot UEM, several factors lead to two major considerations: first, that a large area photoemission source is required to smaller area or even single point emitters, and second, the transverse emittance of the beam must be minimized.

These considerations drive the remainder of this thesis.
In this chapter, I will first convince the reader of these considerations.
As a direct consequence thereof, it is our belief that a successful UEM project cannot simply stem from small modifications to the platform of a conventional electron microscope.
In the following chapters, I will show how we are addressing these considerations for the prototype system at UIC, both in column design (Chapter \ref{chap:prototype}) and photocathode engineering (Chapter \ref{chap:photocathode}).

@@

In a conventional electron microscope the electrons are generated by one of several processes, often by heating the cathode or applying a large field to the cathode, or combinations thereof.
Although these processes produce a very large number of electrons, far more than required by the Rose criterion, they are essentially not highly directional.
A pinhole is used to eliminate most of the electrons, with the exception of those which will travel down the column axis, thereby reducing the beam current but producing a high-quality beam.
%TODO ref(s)
For conventional electron microscopes without time resolution, the Rose criterion may be met for arbitrarily low beam current by simply allowing the image to acquire for a long enough time to collect sufficent electrons.
Further, high beam current may be damaging to the sample over time, so a lower beam current is often preferred.

By definition, for single-shot imaging with a DTEM, all of the electrons used to form an image must be contained in a single pulse.
In a single-shot DTEM, destructive measurements will usually result in useful images, in fact, the dynamics being studied are often destructive, regardless of the knock-on damage cause by the probe.
However, although sample damage concerns may be neglected, the use of a pinhole is likely to reduce the pulse charge below the useful level.
This means that the designer of a DTEM must endeavor to retain and utilize all of the generated electrons.
